### 2021-03-09 results/draft.tex
added

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology. Environmental DNA (eDNA)

>>>>

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
Field survey using environmental DNA (eDNA) is recently widely used for detecting invesive or rare species and hotspot of biodiversity because eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling method such as visual.
%Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
The presence/absence of eDNA, however, includes many types of
